How to Prepare Your Papers for the JIP

### 2018-06-06 SJIS/tech-esample.tex
Copied SWoPP template into the directory.

\documentclass[JIP]{ipsj}

\usepackage{graphicx}
\usepackage{latexsym}

@@

\setcounter{volume}{22}% vol22=2014
\setcounter{number}{4}% 1=Jan., 2=Apr., 3=July, 4=Oct.
\setcounter{page}{1}

\received{2014}{3}{4}
%\rereceived{2011}{10}{1}   % optional
%\rerereceived{2011}{10}{31} % optional
\accepted{2014}{8}{1}

@@

\title{How to Prepare Your Papers for the JIP\\
(ipsj.cls version 1.7)}

@@

\author{Taro Joho}{IPSJ,PJU}[joho.taro@ipsj.or.jp]
\author{Hanako Shori}{JU}[shori.hanako@johosyori-u.ac.jp]
\author{Jiro Gakkai}{IPSJ}

@@

\begin{keyword}
Journal of Information Processing, \LaTeX, style files, ``Dos and
 Don'ts'' list
\end{keyword}

@@

The JIP author's kit including the \LaTeX style files can be downloaded
from the following URL:
\begin{quote}
 \small
 \|http://www.ipsj.or.jp/jip/submit/style.html|
\end{quote}
The kit includes the following files:
\begin{enumerate}
\item \|ipsj.cls|: style file for ipsj journals
\item \|ipsjpref.sty|: style for the foreword
\item \|jsample.tex|: source for the Japanese version of this guide
\item \|esample.tex|: source of this guide
\item \|ipsjsort-e.bst|: bibtex style (sorted)
\item \|ipsjunsrt-e.bst|: bibtex style (unsorted)
\item \|bibsample.bib|: sample of bibliographic data (Japanese)
\item \|ebibsample.bib|: sample of bibliographic data (English)

\item \|ipsjtech.sty|: style file for technical report
\item \ \|tech-jsample.tex|: source for the Japanese version of technical report
\item \ \|tech-esample.tex|: source for the English version of technical report
\end{enumerate}

@@

The JIP adopts \textit{single blind review}, 
where you will not know reviewers names.

@@

After you receive the notification of acceptance, revise your paper in
accordance with the comments from the referees.
The layout of
figures and tables should be fixed. After that, \textit{check your paper
again and again to completely remove description errors}.

@@

\noindent
\|\documentclass[JIP]{ipsj}|\\
\quad Specify other option styles if necessary.\\
\quad Specify auxiliary styles with \|\usepackage|.\\
\\
\Underline{\|\setcounter{|{\bf volume}\|}{<volume>}|}\\
\Underline{\|\setcounter{|{\bf number}\|}{<number>}|}\\
\Underline{\|\setcounter{|{\bf page}\|}{<first-page>}|}\\
\Underline{\|\|{\bf received}\|{<year>}{<month>}{<day>}|}\\
\Underline{\|\|{\bf accepted}\|{<year>}{<month>}{<day>}|}\\
\quad Define your own macros if necessary.\\\\
\quad If you cannot use the \|txfonts| package, please do not use the following command\\
\Underline{\|\usepackage[varg]{txfonts}|}\\
\Underline{\|\makeatletter|}\\
\Underline{\|\input{ot1txtt.fd}|}\\
\Underline{\|\makeatother|}\\\\
\|\begin{document}|\\[.5em]
\|\title{<title>}|\\[.5em]
\Underline{\|\affiliate{<affiliation-label>}{<affiliation>}|}\\\\
\quad Declare current affiliation with \|\paffilabel| if necessary.\\
\Underline{\|\paffiliate{<affiliation-label>}{<affiliation>}|}\\\\
\Underline{\|\author{1st-author}{affiliation-label}[E-mail]|}\\
\Underline{\|\author{2nd-author}{affiliation-label}|}\\\\
\|\begin{abstract}|\\
\quad\|<abstract>|\\
\|\end{abstract}|\\\\
\|\begin{keyword}|\\
\quad\|<keyword>|\\
\|\end{keyword}|\\\\
\|\maketitle|\\\\
\|\section{|heading-of-1st-section\|}|\\
\dots\dots\dots\dots\dots\\
\quad \|<main text>|\\
\dots\dots\dots\dots\dots\\\\
\quad Put acknowledgments here with the acknowledgment environment if any.\\
\|\begin{acknowledgment}|\\
\|\end{acknowledgment}|\\\\
\|\begin{thebibliography}{99}%9 or 99|\\
\|\bibitem{1}|\\
\|\bibitem{2}|\\
\|\end{thebibliography}|\\\\
\quad Put appendices here following \|\appendix| if any.\\
\|\appendix|\\
\|\section{|heading-of-1st-section\|}|\\\\
\Underline{\|\begin{biography}|}\\
\Underline{\|\profile{<1st-author>}{<biography-of-1st-author>}|}\\
\Underline{\|\profile{<2nd-author>}{<biography-of-2nd-author>}|}\\
\Underline{\|\end{biography}|}\\
\|\end{document}|

@@

\begin{enumerate}
\item\|JIP|\footnote{English should be used for the English version of the Transactions.}
\quad For English documents
\item\|invited| \quad For invited papers
\item\|sigrecommended| \quad For recommended papers
\item\|technote| \quad For technical notes
\item\|preface| \quad For the preface of an issue
\end{enumerate}

@@

If you specify auxiliary style files with the
\|\usepackage|, you must include them in the file package when you send
your final version to the IPSJ\@.

@@

%4.1.1
\subsubsection{Optional style exclusively for technical reports}

In addition to the options described above, 
an option intended exclusively for technical reports is available.
\begin{quote}
\|techrep|\quad technical report
\end{quote}

If \|\documentclass[techrep,JIP]{ipsj}| is used,
the technical-report style will be applied.

@@

%4.3
\subsection{Main part}

%4.3.1
\subsubsection{Sectioning}

@@

%4.3.2
\subsubsection{Fixed Baselines}

@@

%4.3.3
\subsubsection{Font Size}

@@

%4.3.4
\subsubsection{Itemizing}

@@

%4.3.5
\subsubsection{Footnotes}

@@

%4.3.6
\subsubsection{Overfulls and Underfulls}

@@

For underfulls, you will conveniently get the following warning message,
\begin{quote}\footnotesize*
\|Underfull| \|\hbox| \|(badness 10000)| \|detected|
\end{quote}
by inserting \|\\| at the end of a paragraph.  This message is also
output when you use \|\\| just before a list-like environment, just
before an \|\item|, and at the end of the environment. Such underfulls
cause unattractive empty lines and a flood of warnings that will hide
important error messages.

%4.4
\subsection{Formulas}\label{sec:ITEM}

%4.4.1
\subsubsection{In-text Formulas}

@@

%4.4.2
\subsubsection{Displayed Formulas}

@@

%4.4.3
\subsubsection{Eqnarray environment}

@@

%4.4.4
\subsubsection{Special Fonts}

@@

\begin{figure}[tb]%2
\begin{minipage}[t]{0.5\columnwidth}
\footnotesize
\setbox0\vbox{
\hbox{\|\begin{minipage}[t]%|}
\hbox{\|  {0.5\columnwidth}|}
\hbox{\|\captionType{table}|}
\hbox{\|\caption{| \ldots \|}|}
\hbox{\|\ecaption{| \ldots \|}|}
\hbox{\|\label{| \ldots \|}|}
\hbox{\|\makebox[\textwidth][c]{%|}
\hbox{\|\begin{tabular}[t]{lcr}|}
\hbox{\|\hline\hline|}
\hbox{\|left&center&right\\\hline|}
\hbox{\|L1&C1&R1\\|}
\hbox{\|L2&C2&R2\\\hline|}
\hbox{\|\end{tabular}}|}
\hbox{\|\end{minipage}|}}
\hbox{}
\centerline{\fbox{\box0}}
\caption{Contents of table \protect\ref{tab:right}}
\label{fig:left}
\end{minipage}%
\begin{minipage}[t]{0.5\columnwidth}
\CaptionType{table}
\caption{A table built by Fig.\ \protect\ref{fig:left}}
\label{tab:right}
\makebox[\textwidth][c]{\begin{tabular}[t]{lcr}\hline\hline
left&center&right\\\hline
L1&C1&R1\\
L2&C2&R2\\\hline
\end{tabular}}
\end{minipage}
\end{figure}

@@

\begin{figure*}[t]
\setbox0\vbox{\large
\hbox{\|\begin{figure*}[t]|}
\hbox{\quad\|<|figure-body\|>|}
\hbox{\|\caption{<|caption\|>}|}
\hbox{\|\label{| $\ldots$ \|}|}
\hbox{\|\end{figure*}|}}
\centerline{\fbox{\hbox to.9\textwidth{\hss\box0\hss}}}
\caption{Double column figure}
\label{fig:double}
\end{figure*}

%4.5
\subsection{Figures}

@@

%4.6
\subsection{Tables}

@@

%4.7
\subsection{Citations, Reference, Acknowledgements}

%4.7.1
\subsubsection{Citations}

@@

%4.7.2
\subsubsection{List of References}

@@

%4.7.3
\subsubsection{Acknowledgments and Appendices}

If you want to acknowledge people, put your acknowledgments just before
the references and enclose them in the \|acknowledgment| environment.

@@

%4.8
\subsection{Biography}

@@

Generally, photographs used in author biographies should be identification photographs.

The printers will crop these photographs to a size of 30\,mm by 25\,mm. 
Avoid using photographs that contain missing portions of the face or photographs 
in which the outline of the face is difficult to distinguish against the background. 
It is recommended to use photographs that have no background or that 
have light-colored backgrounds. 
When digitally submitting photographs for the author biography, 
the photograph must have a resolution of at least 300\,dpi and must 
have been captured using a camera with at least one megapixel resolution. 
Since photographs for the author biographies will be incorporated into 
digital data by the printers at the time the composition is prepared, 
it is not necessary to digitally insert the photographs into the draft.

%5
\section{Check List of ``Dos and Don'ts''}

%5.1
\subsection{The basics of writing}

@@

%5.2
\subsection{Show novelty and usefulness clearly}

@@

%5.3
\subsection{Concrete attention to writing}

@@

%5.4
\subsection{Regarding references}

@@

%5.5
\subsection{Double submission}

@@

%5.6
\subsection{Check by other researchers}

@@

%5.7
\subsection{Miscellaneous}

\begin{itemize}
\item[$\Box$] After the first review round, do not modify the paper
	      except for the stated conditions for acceptance without
	      the reviewers' approval.

\item[$\Box$] The authors cannot select reviewers.

\item[$\Box$] Fill the self-check sheet carefully before submitting the
	      paper.
\end{itemize}

\newpage%%

%6
\section{Concluding Remarks}

@@

\begin{thebibliography}{99}
\bibitem{companion}%1
Goossens, M., Mittelbach, F. and Samarin, A.:
{\it The LaTeX Companion},
Addison Wesley, Reading, 
Massachusetts (1993).

@@

\bibitem{article1}%3
Itoh, S. and Goto, N.: 
An Adaptive Noiseless Coding for Sources with Big Alphabet Size, 
{\it Trans.\ IEICE},  
Vol.E74, No.9, pp.2495--2503 (1991).

\bibitem{article2}%4
Abrahamson, K., Dadoun, N., Kirkpatrick, D.G. and Przytycka, T.: 
A Simple Parallel Tree Contraction Algorithm, 
{\it J.\ Algorithms},  
Vol.10, No.2,
pp.287--302 (1989).

\bibitem{article3}%5
Yamakami, T.: Exploratory Session Analysis in the Mobile Clickstream, 
{\it IPSJ Digital Courier},  
Vol.3, pp.14--20 (online), \\
\doi{10.2197/ipsjdc.3.14} (2007).

\bibitem{book1}%6
Foley, J.D. et al.: 
Computer Graphics --- Principles and Practice, 
System Programming Series, Addison-Wesley, 
Reading, Massachusetts, 2nd edition (1990).

\bibitem{book2}%7
Chang, C.L. and Lee, R.C.T.: 
Symbolic Logic and Mechanical Theorem Proving, 
Academic Press, New York (1973).

@@

\bibitem{inbook1}%9
Knuth, D.E.: 
Art of Computer Programming,
{\it Fundamental Algorithms}, 
Vol.1, chapter 2, 
pp.371--381, 
Addison-Wesley, 2nd edition (1973).

\bibitem{incollection1}%10
Schwartz, A.J.: 
Subdividing B{\'e}zier Curves and Surfaces, 
{\it Geometric Modeling: Algorithms and New Trends\/} 
(Farin, G.E., ed.), 
SIAM, Philadelphia,
pp.55--66 (1987).

\bibitem{inproceedings1}%11
Baraff, D.:
Curved Surfaces and Coherence for Non-penetrating Rigid Body
Simulation, 
{\it Proc.\ SIGGRAPH '90\/} (Beach, R.J., ed.), 
Dallas,
Texas, ACM, Addison-Wesley, 
pp.19--28 (1990).

\bibitem{inproceedings2}%12
Nakashima, H. et al.: 
OhHelp: A Scalable Domain-Decomposing Dynamic Load
Balancing for Particle-in-Cell Simulations, 
{\it Proc.\ Intl.\ Conf. Supercomputing}, 
pp.90--99 (online),\\
\doi{http://doi.acm.org/10.1145/1542275.1542293} (2009).

@@

\bibitem{proceedings1}%17
Institute for New Generation Computer Technology: 
{\it Proc.\ Intl.\ Conf.\ on Fifth Generation Computer Systems}, 
Vol.1 (1992).

@@

%A.1
\section{How to Write an Appendix}
\label{A1}

@@

%A.1.1
\subsection{Example of a Heading}
The command \|\subsection| in the appendix gives this kind of heading.

%A.2
\section{Commands for Transactions}
\label{A2}

@@

\begin{itemize}
\item \|PRO| (Trans.\ Programming)
\item \|TOM| (Trans.\ Mathematical Modeling and Its Applications)
\item \|TOD| (Trans.\ Database)
\item \|ACS| (Trans.\ Advanced Computing Systems)
\item \|CDS| (Trans.\ Consumer Device \& System)
\item \|DC | (Trans.\ Digital Content)
\item \|TCE| (Trans.\ Computer and Education)
\item \|TBIO| (Bioinformatics)
\item \|SLDM| (System LSI Design Methodology)
\item \|CVA| (Computer Vision and Applications)
\end{itemize}

Moreover, for papers in English, the command \|english| can be added. For
example, writing \|\documentclass[PRO,| \|english]{ipsj}| will create an
English document.

@@

%A.3
\section{Unique Commands for Each Part}

@@

%A.3.1
\subsection{Unique Functions for Programming (PRO)}

Issues of Transactions on Programming (PRO) includes not only regular
papers but also abstracts from research presentations delivered in the
research groups of SIGPRO\@. The file for an abstract consists of
material from the \|\documentclass| to the \maketitle of the format
shown in Section~\ref{body}. That is, the file does not have a main
text. Note that the reception and acceptance dates are not required, but
the date of presentation has to be given:
\begin{quote}
\|\Presented{<year>}{<month>}{<day>}|
\end{quote}

%A.3.2
\subsection{Unique Functions for Database (TOD)}

@@

%A.3.3
\subsection{Unique Functions for Consumer Devices \& Systems (CDS)}

@@

The types are:
\begin{itemize}
\item \|systems  | Paper on Consumer Systems
\item \|services | Paper on Consumer Services
\item \|devices  | Paper on Consumer Devices
\item \|Research | Research Paper
\end{itemize}
For English papers, you simply need to add \|english|.

%A.3.4
\subsection{Unique Functions for Digital Content (DCON)}

In the ``Transactions on Digital Content,'' since the
headings differ depending on the type of document, the type of heading
is to be changed with the option.

The types are:
\begin{itemize}
\item \|Research | Research Paper
\item \|Practice | Practice Paper
\item \|Content  | Content Paper
\end{itemize}
For English papers, you simply need to add \|english|.

%A.3.5
\subsection{Unique Functions for Computer and Education (TCE)}

In the ``Transactions on Computer and Education,'' since the headings
differ depending on the type of document, the type of heading is
to be changed with the option.

The types are:
\begin{itemize}
\item \|No specification  | Regular Paper (Default)
\item \|Short             | Short Paper
\end{itemize}
For English papers, you simply need to add \|english|.

%A.3.6
\subsection{Unique Functions for Bioinformatics (TBIO)}

@@

%A.3.7
\subsection{Unique Functions for Computer Vision and Applications (CVA)}

@@

There are three classes of documents:
\begin{itemize}
\item \|No specification | Regular Paper (Default)
\item \|Research         | Research Paper
\item \|system           | Systems Paper
\item \|Express          | Express Paper
\end{itemize}

@@

%A.3.8
\subsection{Unique Functions for System LSI Design Methodology (SLDM)}

@@

There are two classes of documents:
\begin{itemize}
\item \|No specification | Regular Paper (Default)
\item \|Short            | Short Paper
\end{itemize}

@@

\begin{biography}
\profile{Taro Joho}{was born in 1970. He received his M.S.\ degree from
Johoshori University in 1994.
He joined
the Information
Processing Society of Japan in 1994.
He is currently an associate professor at
\mbox{Johoshori} University.
His research interest is online
publishing systems. He is a member of the IEEE and ACM\@.}
%
\profile{Hanako Shori}{was born in 1960. She received her M.E.\ and
Ph.D.\ from Johoshori University in 1984 and 1987, respectively. She
became an associate professor at Gakkai University in 1992 and a
professor at Johoshori University in 1997. Her current research
interest is online publishing systems. She received the Kiyasu Kinen
award in 2010. She is a Board Member of the IPSJ and a member of the
IEICE, IEEE-CS, and ACM\@.} 
%
\profile{Jiro Gakkai}{was born in 1970. He received his M.S.\ degree
from Johoshori University in 1994 and has been engaged in the
Information Processing Society of Japan since 1994. His research
interest is online publishing systems. He is a member of the IEEE and
ACM\@.}
%
\end{biography}
\end{document}

>>>>

%%
%% 研究報告用スイッチ
%% [techrep]
%%
%% 欧文用スイッチ(keywordは任意)
%% [english]
%%

\documentclass[techrep,english]{ipsj}

\usepackage[dvips]{graphicx}
\usepackage{latexsym}

@@

\setcounter{volume}{21}% vol21=2013
\setcounter{number}{1}
\setcounter{page}{1}

%\received{2011}{7}{1}
%\rereceived{2011}{10}{1}   % optional
%\rerereceived{2011}{10}{31} % optional
%\accepted{2011}{11}{5}

@@

\title{How to Prepare Your Papers for the JIP}

@@

\author{Joho Taro}{IPSJ,PJU}[joho.taro@ipsj.or.jp]
\author{Shori Hanako}{JU}[shori.hanako@johosyori-u.ac.jp]
\author{Gakkai Jiro}{JU}

@@

%\begin{keyword}
%Journal of Information Processing, \LaTeX, style files, ``Dos and
% Don'ts'' list
%\end{keyword}

@@

The JIP author's kit including the \LaTeX style files can be downloaded
from the following URL:
\begin{quote}
 \small
 \|http://www.ipsj.or.jp/jip/submit/style.html|
\end{quote}
The kit includes the following files:
\begin{enumerate}%{
\item \|ipsj.cls|: style file for ipsj journals
\item \|ipsjdraft.sty|: style for drafts to be submitted
\item \|ipsjpref.sty|: style for the foreword
\item \|jsample.tex|: source for the Japanese version of this guide
\item \|esample.tex|: source of this guide
\item \|ipsjsort-e.bst|: bibtex style (sorted)
\item \|ipsjunsrt-e.bst|: bibtex style (unsorted)
\item \|bibsample.bib|: sample of bibliographic data (Japanese)
\item \|ebibsample.bib|: sample of bibliographic data (English)
\end{enumerate}%}

@@

The JIP adopts \textit{double blind review}, where reviewers of your
paper will not know your name, and you will not know theirs.  To ensure
that this is possible, the submitted draft version should not contain
information about the authors.

@@

After you receive the notification of acceptance, revise your paper in
accordance with the comments from the referees and add the required
omissions from the draft, such as a biography, if any. The layout of
figures and tables should be fixed. After that, \textit{check your paper
again and again to completely remove description errors}.

@@

\noindent
\|\documentclass[JIP]{ipsj}|\ or\\
\|\documentclass[JIP,draft]{ipsj}|\\
\quad Specify other option styles if necessary.\\
\quad Specify auxiliary styles with \|\usepackage|.\\
\\
\Underline{\|\setcounter{|{\bf volume}\|}{<volume>}|}\\
\Underline{\|\setcounter{|{\bf number}\|}{<number>}|}\\
\Underline{\|\setcounter{|{\bf page}\|}{<first-page>}|}\\
\Underline{\|\|{\bf received}\|{<year>}{<month>}{<day>}|}\\
\Underline{\|\|{\bf accepted}\|{<year>}{<month>}{<day>}|}\\
\quad Define your own macros if necessary.\\\\
\quad If you cannot use the \|txfonts| package, please do not use the following command\\
\Underline{\|\usepackage[varg]{txfonts}|}\\
\Underline{\|\makeatletter|}\\
\Underline{\|\input{ot1txtt.fd}|}\\
\Underline{\|\makeatother|}\\\\
\|\begin{document}|\\[.5em]
\|\title{<title>}|\\[.5em]
\Underline{\|\affiliate{<affiliation-label>}{<affiliation>}|}\\\\
\quad Declare current affiliation with \|\paffilabel| if necessary.\\
\Underline{\|\paffiliate{<affiliation-label>}{<affiliation>}|}\\\\
\Underline{\|\author{1st-author}{affiliation-label}[E-mail]|}\\
\Underline{\|\author{2nd-author}{affiliation-label}|}\\\\
\|\begin{abstract}|\\
\quad\|<abstract>|\\
\|\end{abstract}|\\\\
\|\begin{keyword}|\\
\quad\|<keyword>|\\
\|\end{keyword}|\\\\
\|\maketitle|\\\\
\|\section{|heading-of-1st-section\|}|\\
\dots\dots\dots\dots\dots\\
\quad \|<main text>|\\
\dots\dots\dots\dots\dots\\\\
\quad Put acknowledgments here with the acknowledgment environment if any.\\
\|\begin{acknowledgment}|\\
\|\end{acknowledgment}|\\\\
\|\begin{thebibliography}{99}%9 or 99|\\
\|\bibitem{1}|\\
\|\bibitem{2}|\\
\|\end{thebibliography}|\\\\
\quad Put appendices here following \|\appendix| if any.\\
\|\appendix|\\
\|\section{|heading-of-1st-section\|}|\\\\
\Underline{\|\begin{biography}|}\\
\Underline{\|\profile{<1st-author>}{<biography-of-1st-author>}|}\\
\Underline{\|\profile{<2nd-author>}{<biography-of-2nd-author>}|}\\
\Underline{\|\end{biography}|}\\
\|\end{document}|

@@

\begin{enumerate}
\item\|JIP| For English documents
\item\|draft| For draft versions
\item\|invited| For invited papers
\item\|sigrecommended| For a paper recommended by a SIG
\item\|technote| For technical notes
\item\|preface| For the preface of an issue
\end{enumerate}

@@

If you use \|\documentclass[JIP,draft]{ipsj}|, the ``draft'' option
style will be applied.  If you specify auxiliary style files with the
\|\usepackage|, you must include them in the file package when you send
your final version to the IPSJ\@.

@@

@@

%5
\section{Main part}
%5.1
\subsection{Sectioning}

@@

%5.2
\subsection{Fixed Baselines}

@@

%5.3
\subsection{Font Size}

@@

%5.4
\subsection{Itemizing}\label{sec:item*}

@@

%5.5
\subsection{Footnotes}

@@

%5.5.1
\subsubsection{Overfulls and Underfulls}

@@

For underfulls, you will conveniently get the following warning message,
\begin{quote}\footnotesize*
\|Underfull| \|\hbox| \|(badness 10000)| \|detected|
\end{quote}
, by inserting \|\\| at the end of a paragraph.  This message is also
output when you use \|\\| just before a list-like environment, just
before an \|\item|, and at the end of the environment. Such underfulls
cause unattractive empty lines and a flood of warnings that will hide
important error messages.

%5.6
\subsection{Formulas}\label{sec:ITEM}
%5.6.1
\subsubsection{In-text Formulas}

@@

%5.6.2
\subsubsection{Displayed Formulas}

@@

%5.6.3
\subsubsection{Eqnarray environment}

@@

%5.6.4
\subsubsection{Special Fonts}

@@

\begin{figure}[tb]%2
\begin{minipage}[t]{0.5\columnwidth}
\footnotesize
\setbox0\vbox{
\hbox{\|\begin{minipage}[t]%|}
\hbox{\|  {0.5\columnwidth}|}
\hbox{\|\captionType{table}|}
\hbox{\|\caption{| \ldots \|}|}
\hbox{\|\ecaption{| \ldots \|}|}
\hbox{\|\label{| \ldots \|}|}
\hbox{\|\makebox[\textwidth][c]{%|}
\hbox{\|\begin{tabular}[t]{lcr}|}
\hbox{\|\hline\hline|}
\hbox{\|left&center&right\\\hline|}
\hbox{\|L1&C1&R1\\|}
\hbox{\|L2&C2&R2\\\hline|}
\hbox{\|\end{tabular}}|}
\hbox{\|\end{minipage}|}}
\hbox{}
\centerline{\fbox{\box0}}
\caption{Contents of Table \protect\ref{tab:right}}
\label{fig:left}
\end{minipage}%
\begin{minipage}[t]{0.5\columnwidth}
\CaptionType{table}
\caption{A table built by Fig.\ \protect\ref{fig:left}}
\label{tab:right}
\makebox[\textwidth][c]{\begin{tabular}[t]{lcr}\hline\hline
left&center&right\\\hline
L1&C1&R1\\
L2&C2&R2\\\hline
\end{tabular}}
\end{minipage}
\end{figure}

@@

\begin{figure*}[t]
\setbox0\vbox{\large
\hbox{\|\begin{figure}*[t]|}
\hbox{\quad\|<|figure-body\|>|}
\hbox{\|\caption{<|caption\|>}|}
\hbox{\|\label{| $\ldots$ \|}|}
\hbox{\|\end{figure*}|}}
\centerline{\fbox{\hbox to.9\textwidth{\hss\box0\hss}}}
\caption{Double column figure}
\label{fig:double}
\end{figure*}

%5.7
\subsection{Figures}

@@

%5.8
\subsection{Tables}

@@

%5.9
\subsection{Citations, Reference, Acknowledgements}
%5.9.1
\subsubsection{Citations}

@@

%5.9.2
\subsubsection{List of References}

@@

%5.9.3
\subsubsection{Acknowledgments and Appendices}

If you want to acknowledge people, put your acknowledgments just before
the references and enclose them in the \|acknowledgment|
environment. Acknowledgments will not be printed in drafts.

@@

%5.10
\subsection{Biography}

@@

%6
\section{Check List of ``Dos and Don'ts''}
%6.1
\subsection{The basics of writing}

@@

%6.2
\subsection{Show novelty and usefulness clearly}

@@

%6.3
\subsection{Concrete attention to writing}

@@

%6.4
\subsection{Regarding references}

@@

%6.5
\subsection{Double submission}

@@

%6.6
\subsection{Check by other researchers}

@@

%6.7
\subsection{Miscellaneous}

\begin{itemize}
\item[$\Box$] After the first review round, do not modify the paper
	      except for the stated conditions for acceptance without
	      the reviewers' approval.
\item[$\Box$] Since the IPSJ uses a double-blind review system, in which
	      both author(s) and reviewers remain anonymous, the authors
	      cannot select reviewers.
\item[$\Box$] Fill the self-check sheet carefully before submitting the
	      paper.
\end{itemize}

%7
\section{Concluding Remarks}

@@

\begin{thebibliography}{99}
\bibitem{companion}%1
Goossens, M., Mittelbach, F., and Samarin, A.:
{\it The LaTeX Companion},
Addison Wesley, Reading, 
Massachusetts (1993).

@@

\bibitem{article1}%3
Itoh, S. and Goto, N.: 
An Adaptive Noiseless Coding for Sources with Big
Alphabet Size, 
{\it Trans.\ IEICE},  
Vol. E74, No. 9, pp. 2495--2503 (1991).

\bibitem{article2}%4
Abrahamson, K., Dadoun, N., Kirkpatrick, D.G., and Przytycka, T.: 
A Simple Parallel Tree Contraction Algorithm, 
{\it J.\ Algorithms},  
Vol. 10, No. 2,
pp. 287--302 (1989).

\bibitem{article3}%5
Yamakami, T.: Exploratory Session Analysis in the Mobile Clickstream, 
{\it IPSJ Digital Courier},  
Vol. 3, pp. 14--20 (online), \\
\doi{10.2197/ipsjdc.3.14} (2007).

\bibitem{book1}%6
Foley, J.D. et al.: 
{\it Computer Graphics --- Principles and Practice},
System Programming Series, Addison-Wesley, 
Reading, Massachusetts, 2nd edition (1990).

\bibitem{book2}%7
Chang, C.L. and Lee, R.C.T.: 
{\it Symbolic Logic and Mechanical Theorem Proving}, 
Academic Press, New York (1973).

@@

\bibitem{inbook1}%9
Knuth, D.E.: 
{\it Fundamental Algorithms}, 
Art of Computer Programming,
Vol. 1, chapter 2, 
pp. 371--381, 
Addison-Wesley, 2nd edition (1973).

\bibitem{incollection1}%10
Schwartz, A.J.: 
Subdividing B{\'e}zier Curves and Surfaces, 
{\it Geometric Modeling: Algorithms and New Trends\/} 
(Farin, G.E., ed.), 
SIAM, Philadelphia,
pp. 55--66 (1987).

\bibitem{inproceedings1}%11
Baraff, D.:
Curved Surfaces and Coherence for Non-penetrating Rigid Body
Simulation, 
{\it SIGGRAPH '90 Proceedings\/} (Beach, R.J., ed.), 
Dallas,
Texas, ACM, Addison-Wesley, 
pp. 19--28 (1990).

\bibitem{inproceedings2}%12
Nakashima, H. et al.: 
OhHelp: A Scalable Domain-Decomposing Dynamic Load
Balancing for Particle-in-Cell Simulations, 
{\it Proc.\ Intl.\ Conf. Supercomputing}, 
pp. 90--99 (online),\\
\doi{http://doi.acm.org/10.1145/1542275.1542293} (2009).

@@

\bibitem{proceedings1}%17
Institute for New Generation Computer Technology: 
{\it Proc.\ Intl.\ Conf.\ on Fifth Generation Computer Systems}, 
Vol. 1 (1992).

@@

%8
\section{How to Write an Appendix}
\label{A1}

@@

%8.1
\subsection{Example of a Heading}
The command \|\subsection| in the appendix gives this kind of heading.

%9
\section{Commands for Transactions}
\label{A2}

@@

\begin{itemize}
\item \|PRO| (Trans.\ Programming)
\item \|TOM| (Trans.\ Mathematical Modeling and Its Applications)
\item \|TOD| (Trans.\ Database)
\item \|ACS| (Trans.\ Advanced Computing Systems)
\item \|CDS| (Trans.\ Consumer Device \& System)
\item \|TBIO| (Bioinformatics)
\item \|SLDM| (System LSI Design Methodology)
\item \|CVA| (Computer Vision and Applications)
\end{itemize}

Moreover, for papers in English, the command English can be added. For
example, writing \|\documentclass[PRO,| \|english]{ipsj}| will create an
English document.

@@

%10
\section{Unique Commands for Each Part}

@@

%10.1
\subsection{Unique Functions for Programming (PRO)}

Issues of Transactions on Programming (PRO) includes not only regular
papers but also abstracts from research presentations delivered in the
research groups of SIGPRO\@. The file for an abstract consists of
material from the \|\documentclass| to the \maketitle of the format
shown in Section~\ref{body}. That is, the file does not have a main
text. Note that the reception and acceptance dates are not required, but
the date of presentation has to be given:
\begin{quote}
\|\Presents{<year>}{<month>}{<day>}|
\end{quote}

%10.2
\subsection{Unique Functions for Database (TOD)}

@@

%10.3
\subsection{Unique Functions for Consumer Devices \& Systems (CDS)}

@@

The types are:
\begin{itemize}
\item \|systems  | Paper on Consumer Systems
\item \|services | Paper on Consumer Services
\item \|devices  | Paper on Consumer Devices
\item \|research | Research Paper
\end{itemize}
For English papers, you simply need to add English.

%10.4
\subsection{Unique Functions for Bioinformatics (TBIO)}

@@

%10.5
\subsection{Unique Functions for Computer Vision and Applications (CVA)}

@@

There are three classes of documents:
\begin{itemize}
\item \|No specification | Regular Paper (Default)
\item \|Research | Research Paper
\item \|system   | Systems Paper
\end{itemize}

@@

%10.6
\subsection{Unique Functions for System LSI Design Methodology (SLDM)}

@@

There are two classes of documents:
\begin{itemize}
\item \|No specification| Regular Paper (Default)
\item \|Short| Short Paper
\end{itemize}

@@

%% 以降無視されます

\begin{biography}
\profile{Joho Taro}{was born in 1970. He received his M.S.\ degree from
 Johoshori University in 1994 and has been engaged in the Information
 Processing Society of Japan since 1994. His research interest is online
 publishing systems. He is a member of the IEEE and ACM\@.}
%
\profile{Shori Hanako}{was born in 1960. She received her M.E.\ and
 Ph.D.\ from Johoshori University in 1984 and 1987, respectively. She
 became an associate professor at Gakkai University in 1992 and a
 professor at Johoshori University in 1997. Her current research
 interest is online publishing systems. She received the Kiyasu Kinen
 award in 2010. She is a Board Member of the IPSJ and a member of the
 IEICE, IEEE-CS, and ACM\@.} 
%
\profile{Gakkai Jiro}{was born in 1970. He received his M.S.\ degree
 from Johoshori University in 1994 and has been engaged in the
 Information Processing Society of Japan since 1994. His research
 interest is online publishing systems. He is a member of the IEEE and
 ACM\@.}
%
\end{biography}
\end{document}
